Sparsely Activated Networks

### 2023-06-27 latex/ms.tex
.

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys-values}{python/bin/keys-values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-identity-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-relu-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-top-k-absolutes-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-pool-indices-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-identity-2d-2-activations-1.png}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-relu-2d-2-activations-0.png}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-top-k-absolutes-2d-2-activations-0.png}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-pool-indices-2d-2-activations-0.png}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-2d-2-activations-0.png}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.png}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-1.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-1.png}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-1.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-1.png}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{python/bin/apnea-ecg.png}
	\includegraphics[width=0.245\textwidth]{python/bin/bidmc.png}
	\includegraphics[width=0.245\textwidth]{python/bin/bpssrat.png}
	\includegraphics[width=0.245\textwidth]{python/bin/cebsdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/ctu-uhb-ctgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/drivedb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/emgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/mitdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/noneeg.png}
	\includegraphics[width=0.245\textwidth]{python/bin/prcp.png}
	\includegraphics[width=0.245\textwidth]{python/bin/shhpsgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/slpdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/sufhsdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/voiced.png}
	\includegraphics[width=0.245\textwidth]{python/bin/wrist.png}
	\includegraphics[width=0.245\textwidth]{python/bin/legend.png}
	\caption{Inverse compression ratio ($CR^{-1}$) vs.\ normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{python/bin/crrl-density-plot.png}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-validation-epochs.png}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-variable-kernel-size-list.png}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-relu-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-top-k-absolutes-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-extrema-pool-indices-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-extrema-1d-1-kernel-0.png}

>>>>

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys-values}{python/tmp/keys-values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{python/tmp/UCI-epilepsy-identity-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/tmp/UCI-epilepsy-relu-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/tmp/UCI-epilepsy-top-k-absolutes-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/tmp/UCI-epilepsy-extrema-pool-indices-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/tmp/UCI-epilepsy-extrema-1d-2-activations-0.png}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{python/tmp/MNIST-identity-2d-2-activations-1.png}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{python/tmp/MNIST-relu-2d-2-activations-0.png}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{python/tmp/MNIST-top-k-absolutes-2d-2-activations-0.png}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{python/tmp/MNIST-extrema-pool-indices-2d-2-activations-0.png}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{python/tmp/MNIST-extrema-2d-2-activations-0.png}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-similarity-0.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-similarity-0.png}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/UCI-epilepsy-extrema-1d-2-similarity-1.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/UCI-epilepsy-extrema-1d-2-kernel-1.png}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/tmp/MNIST-extrema-2d-2-similarity-1.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/tmp/MNIST-extrema-2d-2-kernel-1.png}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{python/tmp/apnea-ecg.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/bidmc.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/bpssrat.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/cebsdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/tmp/ctu-uhb-ctgdb.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/drivedb.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/emgdb.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/mitdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/tmp/noneeg.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/prcp.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/shhpsgdb.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/slpdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/tmp/sufhsdb.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/voiced.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/wrist.png}
	\includegraphics[width=0.245\textwidth]{python/tmp/legend.png}
	\caption{Inverse compression ratio ($CR^{-1}$) vs.\ normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{python/tmp/crrl-density-plot.png}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{python/tmp/mean-flithos-validation-epochs.png}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{python/tmp/mean-flithos-variable-kernel-size-list.png}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{python/tmp/apnea-ecg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bidmc-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bpssrat-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/cebsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/ctu-uhb-ctgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/drivedb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/emgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/mitdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/noneeg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/prcp-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/shhpsgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/slpdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/sufhsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/voiced-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/wrist-relu-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/tmp/apnea-ecg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bidmc-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bpssrat-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/cebsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/ctu-uhb-ctgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/drivedb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/emgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/mitdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/noneeg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/prcp-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/shhpsgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/slpdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/sufhsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/voiced-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/wrist-top-k-absolutes-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/tmp/apnea-ecg-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bidmc-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bpssrat-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/cebsdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/ctu-uhb-ctgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/drivedb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/emgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/mitdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/noneeg-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/prcp-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/shhpsgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/slpdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/sufhsdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/voiced-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/wrist-extrema-pool-indices-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/tmp/apnea-ecg-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bidmc-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/bpssrat-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/cebsdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/ctu-uhb-ctgdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/drivedb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/emgdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/mitdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/noneeg-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/prcp-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/shhpsgdb-extrema-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/tmp/slpdb-extrema-1d-1-kernel-0.png}
